### 2020-04-15 rR.tex
almost done with the results section

% Created by tikzDevice version 0.12.3 on 2020-04-14 11:43:25
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
	( 30.56,248.48) --
	( 33.80,249.35) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.01) --
	( 56.51,256.02) --
	( 59.75,257.05) --
	( 63.00,258.09) --
	( 66.24,259.16) --
	( 69.48,260.24) --
	( 72.73,261.35) --
	( 75.97,262.47) --
	( 79.22,263.61) --
	( 82.46,264.77) --
	( 85.70,265.96) --
	( 88.95,267.16) --
	( 92.19,268.37) --
	( 95.43,269.61) --
	( 98.68,270.86) --
	(101.92,272.13) --
	(105.17,273.42) --
	(108.41,274.73) --
	(111.65,276.06) --
	(114.90,277.41) --
	(118.14,278.78) --
	(121.39,280.18) --
	(124.63,281.60) --
	(127.87,283.02) --
	(131.12,284.47) --
	(134.36,285.93) --
	(137.61,287.42) --
	(140.85,288.93) --
	(144.09,290.46) --
	(147.34,292.01) --
	(150.58,293.60) --
	(153.82,295.21) --
	(157.07,296.86) --
	(160.31,298.52) --
	(163.56,300.20) --
	(166.80,301.90) --
	(170.04,303.62) --
	(173.29,305.37) --
	(176.53,307.15) --
	(179.78,308.95) --
	(183.02,310.78) --
	(186.26,312.65) --
	(189.51,314.56) --
	(192.75,316.49) --
	(196.00,318.45) --
	(199.24,320.44) --
	(202.48,322.45) --
	(205.73,324.50) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.34) --
	(238.17,346.70) --
	(241.41,349.10) --
	(244.65,351.53) --
	(247.90,353.98) --
	(251.14,356.47) --
	(254.39,358.99) --
	(257.63,361.55) --
	(260.87,364.13) --
	(264.12,366.75) --
	(267.36,369.40) --
	(270.60,372.08) --
	(273.85,374.79) --
	(277.09,377.53) --
	(280.34,380.31) --
	(283.58,383.11);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
	( 30.56,248.47) --
	( 33.80,249.35) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.05) --
	( 63.00,258.10) --
	( 66.24,259.17) --
	( 69.48,260.25) --
	( 72.73,261.36) --
	( 75.97,262.48) --
	( 79.22,263.63) --
	( 82.46,264.79) --
	( 85.70,265.97) --
	( 88.95,267.17) --
	( 92.19,268.39) --
	( 95.43,269.63) --
	( 98.68,270.88) --
	(101.92,272.15) --
	(105.17,273.44) --
	(108.41,274.75) --
	(111.65,276.08) --
	(114.90,277.43) --
	(118.14,278.80) --
	(121.39,280.20) --
	(124.63,281.61) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.01) --
	(150.58,293.59) --
	(153.82,295.20) --
	(157.07,296.84) --
	(160.31,298.50) --
	(163.56,300.18) --
	(166.80,301.87) --
	(170.04,303.59) --
	(173.29,305.33) --
	(176.53,307.10) --
	(179.78,308.90) --
	(183.02,310.74) --
	(186.26,312.60) --
	(189.51,314.51) --
	(192.75,316.44) --
	(196.00,318.40) --
	(199.24,320.39) --
	(202.48,322.41) --
	(205.73,324.45) --
	(208.97,326.53) --
	(212.21,328.64) --
	(215.46,330.78) --
	(218.70,332.95) --
	(221.95,335.17) --
	(225.19,337.42) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.35) --
	(238.17,346.73) --
	(241.41,349.13) --
	(244.65,351.57) --
	(247.90,354.04) --
	(251.14,356.54) --
	(254.39,359.07) --
	(257.63,361.64) --
	(260.87,364.24) --
	(264.12,366.87) --
	(267.36,369.54) --
	(270.60,372.24) --
	(273.85,374.97) --
	(277.09,377.73) --
	(280.34,380.52) --
	(283.58,383.35);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
	( 30.56,248.46) --
	( 33.80,249.34) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.11) --
	( 66.24,259.17) --
	( 69.48,260.26) --
	( 72.73,261.37) --
	( 75.97,262.49) --
	( 79.22,263.64) --
	( 82.46,264.80) --
	( 85.70,265.98) --
	( 88.95,267.18) --
	( 92.19,268.40) --
	( 95.43,269.64) --
	( 98.68,270.89) --
	(101.92,272.16) --
	(105.17,273.45) --
	(108.41,274.76) --
	(111.65,276.09) --
	(114.90,277.44) --
	(118.14,278.81) --
	(121.39,280.21) --
	(124.63,281.62) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.00) --
	(150.58,293.58) --
	(153.82,295.19) --
	(157.07,296.83) --
	(160.31,298.48) --
	(163.56,300.16) --
	(166.80,301.85) --
	(170.04,303.57) --
	(173.29,305.31) --
	(176.53,307.07) --
	(179.78,308.87) --
	(183.02,310.70) --
	(186.26,312.57) --
	(189.51,314.47) --
	(192.75,316.41) --
	(196.00,318.37) --
	(199.24,320.36) --
	(202.48,322.38) --
	(205.73,324.43) --
	(208.97,326.51) --
	(212.21,328.63) --
	(215.46,330.77) --
	(218.70,332.96) --
	(221.95,335.18) --
	(225.19,337.44) --
	(228.43,339.73) --
	(231.68,342.05) --
	(234.92,344.41) --
	(238.17,346.80) --
	(241.41,349.22) --
	(244.65,351.67) --
	(247.90,354.15) --
	(251.14,356.67) --
	(254.39,359.22) --
	(257.63,361.81) --
	(260.87,364.43) --
	(264.12,367.08) --
	(267.36,369.77) --
	(270.60,372.48) --
	(273.85,375.24) --
	(277.09,378.02) --
	(280.34,380.84) --
	(283.58,383.69);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] ( 70.02,264.40) --
	( 73.39,258.58) --
	( 66.66,258.58) --
	cycle;

\path[fill=fillColor] ( 78.57,267.35) --
	( 81.93,261.52) --
	( 75.20,261.52) --
	cycle;

\path[fill=fillColor] ( 87.11,270.41) --
	( 90.47,264.59) --
	( 83.75,264.59) --
	cycle;

\path[fill=fillColor] ( 95.65,273.62) --
	( 99.01,267.79) --
	( 92.29,267.79) --
	cycle;

@@

\path[fill=fillColor] (121.28,284.03) --
	(124.64,278.21) --
	(117.91,278.21) --
	cycle;

\path[fill=fillColor] (129.82,287.77) --
	(133.18,281.94) --
	(126.46,281.94) --
	cycle;

\path[fill=fillColor] (138.36,291.66) --
	(141.73,285.83) --
	(135.00,285.83) --
	cycle;

\path[fill=fillColor] (146.90,295.73) --
	(150.27,289.90) --
	(143.54,289.90) --
	cycle;

@@

\path[fill=fillColor] (163.99,304.28) --
	(167.35,298.45) --
	(160.63,298.45) --
	cycle;

\path[fill=fillColor] (172.53,308.80) --
	(175.89,302.97) --
	(169.17,302.97) --
	cycle;

\path[fill=fillColor] (181.07,313.61) --
	(184.44,307.78) --
	(177.71,307.78) --
	cycle;

\path[fill=fillColor] (189.62,318.54) --
	(192.98,312.71) --
	(186.25,312.71) --
	cycle;

\path[fill=fillColor] (198.16,323.65) --
	(201.52,317.83) --
	(194.79,317.83) --
	cycle;

\path[fill=fillColor] (206.70,328.94) --
	(210.06,323.11) --
	(203.34,323.11) --
	cycle;

\path[fill=fillColor] (215.24,334.46) --
	(218.61,328.63) --
	(211.88,328.63) --
	cycle;

\path[fill=fillColor] (223.78,340.25) --
	(227.15,334.42) --
	(220.42,334.42) --
	cycle;

\path[fill=fillColor] (232.33,346.20) --
	(235.69,340.38) --
	(228.96,340.38) --
	cycle;

\path[fill=fillColor] (240.87,352.40) --
	(244.23,346.58) --
	(237.51,346.58) --
	cycle;

\path[fill=fillColor] (249.41,358.80) --
	(252.77,352.98) --
	(246.05,352.98) --
	cycle;

\path[fill=fillColor] (257.95,365.62) --
	(261.32,359.79) --
	(254.59,359.79) --
	cycle;

\path[fill=fillColor] (266.50,372.58) --
	(269.86,366.75) --
	(263.13,366.75) --
	cycle;

\path[fill=fillColor] (275.04,379.67) --
	(278.40,373.84) --
	(271.67,373.84) --
	cycle;

\path[fill=fillColor] (283.58,387.25) --
	(286.94,381.43) --
	(280.22,381.43) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

@@

\path[fill=fillColor] ( 67.53,258.02) --
	( 72.52,258.02) --
	( 72.52,263.02) --
	( 67.53,263.02) --
	cycle;

@@

\path[fill=fillColor] ( 84.61,264.04) --
	( 89.61,264.04) --
	( 89.61,269.03) --
	( 84.61,269.03) --
	cycle;

\path[fill=fillColor] ( 93.15,267.25) --
	( 98.15,267.25) --
	( 98.15,272.25) --
	( 93.15,272.25) --
	cycle;

\path[fill=fillColor] (101.70,270.62) --
	(106.69,270.62) --
	(106.69,275.61) --
	(101.70,275.61) --
	cycle;

\path[fill=fillColor] (110.24,274.08) --
	(115.23,274.08) --
	(115.23,279.08) --
	(110.24,279.08) --
	cycle;

@@

\path[fill=fillColor] (127.32,281.40) --
	(132.32,281.40) --
	(132.32,286.40) --
	(127.32,286.40) --
	cycle;

\path[fill=fillColor] (135.86,285.29) --
	(140.86,285.29) --
	(140.86,290.28) --
	(135.86,290.28) --
	cycle;

\path[fill=fillColor] (144.41,289.36) --
	(149.40,289.36) --
	(149.40,294.36) --
	(144.41,294.36) --
	cycle;

@@

\path[fill=fillColor] (161.49,297.85) --
	(166.49,297.85) --
	(166.49,302.85) --
	(161.49,302.85) --
	cycle;

\path[fill=fillColor] (170.03,302.34) --
	(175.03,302.34) --
	(175.03,307.33) --
	(170.03,307.33) --
	cycle;

\path[fill=fillColor] (178.58,307.20) --
	(183.57,307.20) --
	(183.57,312.19) --
	(178.58,312.19) --
	cycle;

\path[fill=fillColor] (187.12,312.13) --
	(192.11,312.13) --
	(192.11,317.12) --
	(187.12,317.12) --
	cycle;

\path[fill=fillColor] (195.66,317.25) --
	(200.66,317.25) --
	(200.66,322.24) --
	(195.66,322.24) --
	cycle;

\path[fill=fillColor] (204.20,322.50) --
	(209.20,322.50) --
	(209.20,327.49) --
	(204.20,327.49) --
	cycle;

\path[fill=fillColor] (212.74,328.04) --
	(217.74,328.04) --
	(217.74,333.04) --
	(212.74,333.04) --
	cycle;

\path[fill=fillColor] (221.29,333.85) --
	(226.28,333.85) --
	(226.28,338.85) --
	(221.29,338.85) --
	cycle;

\path[fill=fillColor] (229.83,339.77) --
	(234.82,339.77) --
	(234.82,344.76) --
	(229.83,344.76) --
	cycle;

\path[fill=fillColor] (238.37,345.99) --
	(243.37,345.99) --
	(243.37,350.98) --
	(238.37,350.98) --
	cycle;

\path[fill=fillColor] (246.91,352.43) --
	(251.91,352.43) --
	(251.91,357.43) --
	(246.91,357.43) --
	cycle;

\path[fill=fillColor] (255.46,359.42) --
	(260.45,359.42) --
	(260.45,364.42) --
	(255.46,364.42) --
	cycle;

\path[fill=fillColor] (264.00,366.41) --
	(268.99,366.41) --
	(268.99,371.40) --
	(264.00,371.40) --
	cycle;

\path[fill=fillColor] (272.54,373.42) --
	(277.54,373.42) --
	(277.54,378.41) --
	(272.54,378.41) --
	cycle;

\path[fill=fillColor] (281.08,381.10) --
	(286.08,381.10) --
	(286.08,386.09) --
	(281.08,386.09) --
	cycle;

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.52) -- ( 73.56,260.52);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.54) -- ( 90.64,266.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.01) -- ( 87.11,270.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.76) -- ( 99.18,269.76);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.23) -- ( 95.65,273.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.14) -- (107.73,273.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.61) -- (104.19,276.67);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.60) -- (116.27,276.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.07) -- (112.74,280.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.18) -- (124.81,280.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.65) -- (121.28,283.71);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.91) -- (133.35,283.91);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.38) -- (129.82,287.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.80) -- (141.89,287.80);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.26) -- (138.36,291.33);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.88) -- (150.44,291.88);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.34) -- (146.90,295.41);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.31) -- (167.52,300.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.78) -- (163.99,303.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.77) -- (176.06,304.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.23) -- (172.53,308.30);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.68) -- (184.61,309.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.15) -- (181.07,313.21);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.08) -- (189.62,318.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.74) -- (201.69,319.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.21) -- (198.16,323.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.96) -- (210.23,324.96);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.43) -- (206.70,328.50);

>>>>

% Created by tikzDevice version 0.12.3 on 2020-04-14 17:43:43
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 2pt off 2pt ,line join=round] ( 27.31,247.62) --
	( 30.56,248.48) --
	( 33.80,249.35) --
	( 37.04,250.25) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.01) --
	( 56.51,256.02) --
	( 59.75,257.05) --
	( 63.00,258.09) --
	( 66.24,259.16) --
	( 69.48,260.24) --
	( 72.73,261.35) --
	( 75.97,262.47) --
	( 79.22,263.61) --
	( 82.46,264.77) --
	( 85.70,265.96) --
	( 88.95,267.16) --
	( 92.19,268.38) --
	( 95.43,269.61) --
	( 98.68,270.86) --
	(101.92,272.13) --
	(105.17,273.42) --
	(108.41,274.73) --
	(111.65,276.06) --
	(114.90,277.41) --
	(118.14,278.78) --
	(121.39,280.18) --
	(124.63,281.60) --
	(127.87,283.02) --
	(131.12,284.47) --
	(134.36,285.93) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.01) --
	(150.58,293.59) --
	(153.82,295.21) --
	(157.07,296.85) --
	(160.31,298.51) --
	(163.56,300.20) --
	(166.80,301.90) --
	(170.04,303.62) --
	(173.29,305.37) --
	(176.53,307.14) --
	(179.78,308.95) --
	(183.02,310.78) --
	(186.26,312.65) --
	(189.51,314.55) --
	(192.75,316.49) --
	(196.00,318.45) --
	(199.24,320.44) --
	(202.48,322.45) --
	(205.73,324.49) --
	(208.97,326.57) --
	(212.21,328.67) --
	(215.46,330.81) --
	(218.70,332.98) --
	(221.95,335.19) --
	(225.19,337.43) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.34) --
	(238.17,346.71) --
	(241.41,349.11) --
	(244.65,351.53) --
	(247.90,353.99) --
	(251.14,356.48) --
	(254.39,359.01) --
	(257.63,361.56) --
	(260.87,364.15) --
	(264.12,366.77) --
	(267.36,369.42) --
	(270.60,372.10) --
	(273.85,374.82) --
	(277.09,377.56) --
	(280.34,380.34) --
	(283.58,383.15);
\definecolor{drawColor}{RGB}{86,180,233}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 2pt ,line join=round] ( 27.31,247.61) --
	( 30.56,248.47) --
	( 33.80,249.35) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.10) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.10) --
	( 66.24,259.17) --
	( 69.48,260.26) --
	( 72.73,261.36) --
	( 75.97,262.48) --
	( 79.22,263.63) --
	( 82.46,264.79) --
	( 85.70,265.97) --
	( 88.95,267.17) --
	( 92.19,268.39) --
	( 95.43,269.63) --
	( 98.68,270.88) --
	(101.92,272.15) --
	(105.17,273.44) --
	(108.41,274.75) --
	(111.65,276.08) --
	(114.90,277.43) --
	(118.14,278.80) --
	(121.39,280.20) --
	(124.63,281.61) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.45) --
	(147.34,292.00) --
	(150.58,293.58) --
	(153.82,295.19) --
	(157.07,296.84) --
	(160.31,298.49) --
	(163.56,300.17) --
	(166.80,301.87) --
	(170.04,303.59) --
	(173.29,305.33) --
	(176.53,307.10) --
	(179.78,308.90) --
	(183.02,310.73) --
	(186.26,312.60) --
	(189.51,314.50) --
	(192.75,316.44) --
	(196.00,318.40) --
	(199.24,320.39) --
	(202.48,322.40) --
	(205.73,324.45) --
	(208.97,326.53) --
	(212.21,328.63) --
	(215.46,330.78) --
	(218.70,332.95) --
	(221.95,335.17) --
	(225.19,337.42) --
	(228.43,339.70) --
	(231.68,342.01) --
	(234.92,344.36) --
	(238.17,346.74) --
	(241.41,349.14) --
	(244.65,351.58) --
	(247.90,354.06) --
	(251.14,356.56) --
	(254.39,359.10) --
	(257.63,361.67) --
	(260.87,364.27) --
	(264.12,366.91) --
	(267.36,369.58) --
	(270.60,372.28) --
	(273.85,375.01) --
	(277.09,377.78) --
	(280.34,380.58) --
	(283.58,383.41);
\definecolor{drawColor}{RGB}{0,158,115}

\path[draw=drawColor,line width= 1.1pt,dash pattern=on 4pt off 4pt ,line join=round] ( 27.31,247.60) --
	( 30.56,248.46) --
	( 33.80,249.34) --
	( 37.04,250.24) --
	( 40.29,251.16) --
	( 43.53,252.09) --
	( 46.78,253.05) --
	( 50.02,254.02) --
	( 53.26,255.02) --
	( 56.51,256.03) --
	( 59.75,257.06) --
	( 63.00,258.11) --
	( 66.24,259.18) --
	( 69.48,260.26) --
	( 72.73,261.37) --
	( 75.97,262.49) --
	( 79.22,263.64) --
	( 82.46,264.80) --
	( 85.70,265.98) --
	( 88.95,267.19) --
	( 92.19,268.40) --
	( 95.43,269.64) --
	( 98.68,270.89) --
	(101.92,272.16) --
	(105.17,273.45) --
	(108.41,274.76) --
	(111.65,276.09) --
	(114.90,277.44) --
	(118.14,278.81) --
	(121.39,280.21) --
	(124.63,281.62) --
	(127.87,283.04) --
	(131.12,284.48) --
	(134.36,285.94) --
	(137.61,287.42) --
	(140.85,288.92) --
	(144.09,290.44) --
	(147.34,291.99) --
	(150.58,293.57) --
	(153.82,295.18) --
	(157.07,296.82) --
	(160.31,298.48) --
	(163.56,300.15) --
	(166.80,301.85) --
	(170.04,303.56) --
	(173.29,305.30) --
	(176.53,307.07) --
	(179.78,308.87) --
	(183.02,310.70) --
	(186.26,312.56) --
	(189.51,314.47) --
	(192.75,316.41) --
	(196.00,318.37) --
	(199.24,320.36) --
	(202.48,322.38) --
	(205.73,324.43) --
	(208.97,326.51) --
	(212.21,328.63) --
	(215.46,330.77) --
	(218.70,332.96) --
	(221.95,335.18) --
	(225.19,337.45) --
	(228.43,339.74) --
	(231.68,342.07) --
	(234.92,344.42) --
	(238.17,346.82) --
	(241.41,349.24) --
	(244.65,351.70) --
	(247.90,354.18) --
	(251.14,356.71) --
	(254.39,359.26) --
	(257.63,361.85) --
	(260.87,364.48) --
	(264.12,367.14) --
	(267.36,369.83) --
	(270.60,372.55) --
	(273.85,375.31) --
	(277.09,378.11) --
	(280.34,380.93) --
	(283.58,383.79);
\definecolor{fillColor}{RGB}{230,159,0}

@@

\path[fill=fillColor] ( 70.02,264.40) --
	( 73.39,258.57) --
	( 66.66,258.57) --
	cycle;

\path[fill=fillColor] ( 78.57,267.34) --
	( 81.93,261.52) --
	( 75.20,261.52) --
	cycle;

\path[fill=fillColor] ( 87.11,270.42) --
	( 90.47,264.59) --
	( 83.75,264.59) --
	cycle;

\path[fill=fillColor] ( 95.65,273.63) --
	( 99.01,267.80) --
	( 92.29,267.80) --
	cycle;

@@

\path[fill=fillColor] (121.28,284.03) --
	(124.64,278.20) --
	(117.91,278.20) --
	cycle;

\path[fill=fillColor] (129.82,287.78) --
	(133.18,281.95) --
	(126.46,281.95) --
	cycle;

\path[fill=fillColor] (138.36,291.67) --
	(141.73,285.84) --
	(135.00,285.84) --
	cycle;

\path[fill=fillColor] (146.90,295.72) --
	(150.27,289.89) --
	(143.54,289.89) --
	cycle;

@@

\path[fill=fillColor] (163.99,304.26) --
	(167.35,298.43) --
	(160.63,298.43) --
	cycle;

\path[fill=fillColor] (172.53,308.81) --
	(175.89,302.98) --
	(169.17,302.98) --
	cycle;

\path[fill=fillColor] (181.07,313.60) --
	(184.44,307.77) --
	(177.71,307.77) --
	cycle;

\path[fill=fillColor] (189.62,318.53) --
	(192.98,312.70) --
	(186.25,312.70) --
	cycle;

\path[fill=fillColor] (198.16,323.63) --
	(201.52,317.81) --
	(194.79,317.81) --
	cycle;

\path[fill=fillColor] (206.70,328.95) --
	(210.06,323.12) --
	(203.34,323.12) --
	cycle;

\path[fill=fillColor] (215.24,334.48) --
	(218.61,328.65) --
	(211.88,328.65) --
	cycle;

\path[fill=fillColor] (223.78,340.26) --
	(227.15,334.44) --
	(220.42,334.44) --
	cycle;

\path[fill=fillColor] (232.33,346.20) --
	(235.69,340.37) --
	(228.96,340.37) --
	cycle;

\path[fill=fillColor] (240.87,352.35) --
	(244.23,346.52) --
	(237.51,346.52) --
	cycle;

\path[fill=fillColor] (249.41,358.83) --
	(252.77,353.01) --
	(246.05,353.01) --
	cycle;

\path[fill=fillColor] (257.95,365.61) --
	(261.32,359.79) --
	(254.59,359.79) --
	cycle;

\path[fill=fillColor] (266.50,372.59) --
	(269.86,366.77) --
	(263.13,366.77) --
	cycle;

\path[fill=fillColor] (275.04,379.74) --
	(278.40,373.92) --
	(271.67,373.92) --
	cycle;

\path[fill=fillColor] (283.58,387.27) --
	(286.94,381.45) --
	(280.22,381.45) --
	cycle;
\definecolor{fillColor}{RGB}{86,180,233}

@@

\path[fill=fillColor] ( 67.53,258.02) --
	( 72.52,258.02) --
	( 72.52,263.01) --
	( 67.53,263.01) --
	cycle;

@@

\path[fill=fillColor] ( 84.61,264.05) --
	( 89.61,264.05) --
	( 89.61,269.04) --
	( 84.61,269.04) --
	cycle;

\path[fill=fillColor] ( 93.15,267.26) --
	( 98.15,267.26) --
	( 98.15,272.26) --
	( 93.15,272.26) --
	cycle;

\path[fill=fillColor] (101.70,270.61) --
	(106.69,270.61) --
	(106.69,275.61) --
	(101.70,275.61) --
	cycle;

\path[fill=fillColor] (110.24,274.08) --
	(115.23,274.08) --
	(115.23,279.07) --
	(110.24,279.07) --
	cycle;

@@

\path[fill=fillColor] (127.32,281.41) --
	(132.32,281.41) --
	(132.32,286.41) --
	(127.32,286.41) --
	cycle;

\path[fill=fillColor] (135.86,285.30) --
	(140.86,285.30) --
	(140.86,290.30) --
	(135.86,290.30) --
	cycle;

\path[fill=fillColor] (144.41,289.34) --
	(149.40,289.34) --
	(149.40,294.33) --
	(144.41,294.33) --
	cycle;

@@

\path[fill=fillColor] (161.49,297.83) --
	(166.49,297.83) --
	(166.49,302.82) --
	(161.49,302.82) --
	cycle;

\path[fill=fillColor] (170.03,302.36) --
	(175.03,302.36) --
	(175.03,307.36) --
	(170.03,307.36) --
	cycle;

\path[fill=fillColor] (178.58,307.19) --
	(183.57,307.19) --
	(183.57,312.18) --
	(178.58,312.18) --
	cycle;

\path[fill=fillColor] (187.12,312.12) --
	(192.11,312.12) --
	(192.11,317.12) --
	(187.12,317.12) --
	cycle;

\path[fill=fillColor] (195.66,317.22) --
	(200.66,317.22) --
	(200.66,322.21) --
	(195.66,322.21) --
	cycle;

\path[fill=fillColor] (204.20,322.52) --
	(209.20,322.52) --
	(209.20,327.51) --
	(204.20,327.51) --
	cycle;

\path[fill=fillColor] (212.74,328.07) --
	(217.74,328.07) --
	(217.74,333.06) --
	(212.74,333.06) --
	cycle;

\path[fill=fillColor] (221.29,333.88) --
	(226.28,333.88) --
	(226.28,338.88) --
	(221.29,338.88) --
	cycle;

\path[fill=fillColor] (229.83,339.76) --
	(234.82,339.76) --
	(234.82,344.75) --
	(229.83,344.75) --
	cycle;

\path[fill=fillColor] (238.37,345.90) --
	(243.37,345.90) --
	(243.37,350.89) --
	(238.37,350.89) --
	cycle;

\path[fill=fillColor] (246.91,352.51) --
	(251.91,352.51) --
	(251.91,357.51) --
	(246.91,357.51) --
	cycle;

\path[fill=fillColor] (255.46,359.41) --
	(260.45,359.41) --
	(260.45,364.40) --
	(255.46,364.40) --
	cycle;

\path[fill=fillColor] (264.00,366.42) --
	(268.99,366.42) --
	(268.99,371.41) --
	(264.00,371.41) --
	cycle;

\path[fill=fillColor] (272.54,373.53) --
	(277.54,373.53) --
	(277.54,378.53) --
	(272.54,378.53) --
	cycle;

\path[fill=fillColor] (281.08,381.15) --
	(286.08,381.15) --
	(286.08,386.15) --
	(281.08,386.15) --
	cycle;

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.49,260.51) -- ( 73.56,260.51);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 83.58,266.55) -- ( 90.64,266.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.11,263.02) -- ( 87.11,270.08);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 92.12,269.78) -- ( 99.18,269.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.65,266.24) -- ( 95.65,273.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.66,273.13) -- (107.73,273.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (104.19,269.60) -- (104.19,276.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.20,276.59) -- (116.27,276.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.74,273.06) -- (112.74,280.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.75,280.19) -- (124.81,280.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (121.28,276.66) -- (121.28,283.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (126.29,283.92) -- (133.35,283.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.82,280.39) -- (129.82,287.45);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (134.83,287.81) -- (141.89,287.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.36,284.28) -- (138.36,291.35);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (143.37,291.84) -- (150.44,291.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (146.90,288.31) -- (146.90,295.37);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.46,300.29) -- (167.52,300.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (163.99,296.75) -- (163.99,303.82);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (169.00,304.81) -- (176.06,304.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (172.53,301.27) -- (172.53,308.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.54,309.66) -- (184.61,309.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.07,306.13) -- (181.07,313.20);

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (189.62,311.07) -- (189.62,318.14);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.63,319.70) -- (201.69,319.70);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.16,316.17) -- (198.16,323.23);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (203.17,324.99) -- (210.23,324.99);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (206.70,321.46) -- (206.70,328.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (211.71,330.57) -- (218.77,330.57);
